% ==============================================================
% VI-F. QUANTUM HARDWARE VALIDATION
% ==============================================================
% Add this as a new subsection at the end of Section VI (before Section VII)

\subsection{Quantum Hardware Validation}

To validate the quantum phase of Algorithm~\ref{alg:qbb} on physical hardware, we executed the amplitude amplification circuit for four small core-knapsack instances on IBM's \texttt{ibm\_fez} processor (156-qubit Heron~r2, US East) via Qiskit Runtime. Each circuit was run with 8192 shots at optimization level~3.

The instances represent core items remaining after Phase~1 LP variable fixing: 3-item cores (uncorrelated, weakly correlated) and 4-item cores (strongly correlated, subset-sum). For each instance, the quantum oracle marks states achieving the classical optimal value, and amplitude amplification boosts the probability of measuring these optimal states.

Table~\ref{tab:hardware} reports the results. For all four instances, the hardware identified the correct optimal solution as the \textit{most frequently measured state}, confirming that the quantum oracle and amplitude amplification function correctly on real quantum processors without relying on Heuristic~2 or QRAQM.

\begin{table}[htbp]
\caption{IBM Quantum Hardware Results (\texttt{ibm\_fez}, 8192 shots)}
\label{tab:hardware}
\begin{center}
\begin{tabular}{lccccc}
\toprule
\textbf{Instance} & $n$ & \textbf{Iter.} & \textbf{Depth} & \textbf{2Q Gates} & \textbf{HW Prob.} \\
\midrule
Core-3A (Uncorr.) & 3 & 2 & 294 & 72 & 68.7\% \\
Core-3B (Weak.~corr.) & 3 & 2 & 294 & 72 & 69.0\% \\
Core-4A (Strong.~corr.) & 4 & 3 & 2112 & 665 & 17.3\% \\
Core-4B (Subset-sum) & 4 & 3 & 2108 & 661 & 17.4\% \\
\bottomrule
\multicolumn{6}{l}{\footnotesize All instances: optimal solution found as top-1 measured state.} \\
\multicolumn{6}{l}{\footnotesize HW Prob.: probability of measuring the optimal state on hardware.}
\end{tabular}
\end{center}
\end{table}

The 3-qubit instances achieve $\sim$69\% hardware success probability due to shallow circuit depth (294 layers, 72 two-qubit gates). The 4-qubit instances show lower but still decisive success at $\sim$17\%, as circuit depth increases to $\sim$2100 layers with $\sim$660 two-qubit gates. In all cases, the optimal state probability significantly exceeds the uniform baseline ($1/2^n = 12.5\%$ for $n=3$, $6.25\%$ for $n=4$), confirming that amplitude amplification provides measurable enhancement even under hardware noise.

These results demonstrate that the quantum phase of our algorithm is implementable on current-generation quantum processors for small core sizes, providing experimental evidence that complements our theoretical analysis and classical simulation results.
